Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/eval.tex
sec eval pass

@@

Between May 2011 and May 2014, the CVE database\cite{cve-database} lists 83 vulnerabilities when searching for the
string ``ZIP''. Of these, 42 were completely unrelated to the archive format, for example reporting
vulnerabilities revealing Zip codes of other users. 26 vulnerabilities were related to ZIP archives,
but not to input processing, such as trusting arbitrary update ZIP files sent to a server or
vulnerabilities that can be accessed through manipulating files in a ZIP container. This includes
several vulnerabilities allowing another files to replaced while they are extracted from ZIP
files because insufficiently secure temporary directories are used. Of the 15 remaining
vulnerabilities pertaining to ZIP files, 14 vulnerabilities were related to input processing. The
 other vulnerability, which falls outside of Nails purview, concerns a ZIP packer choosing a weak
 legacy cryptosystem even when configured to use AES.

 Nail parsers are immune by design to vulnerabilities like these 14. Ten of those vulnerabilities
 are memory corruption attacks, that could also be avoided by using safer languages or better
 verification tools. Most of the buffer overflows seem to result from inconsistent offset fields
 being manipulated without checking. Because Nail's generated code checks offsets before reading and
 does not expose any untrusted pointers to the application, it protects against memory corruption
 attacks by design.

@@

A similar attack was used by the fourth vulnerability, the infamous Android master key bug
\cite{saurik-masterkey}, that completely by-passed Android security multiple times through parser
differentials between the ZIP handler that checks signatures for privileged applications and the ZIP
implementations that ultimately extracts those files. Thus, valid  application bundles could be
modified to include malicious applications without breaking their signatures. Instead of both
components containing an ad-hoc archive implementation, a single Nail grammar would be reusable
across both implementations.

To provide additional assurance that Nail parsers are free of memory corruption attacks, we ran the
DNS fuzzer provided with the Metasploit\cite{mspframework} framework on our server, which sent
randomly corrupted DNS queries to our server for 4 hours, during which it did not crash or trigger
the stack or heap corruption detector.

>>>>

\paragraph{ZIP analysis.}

@@

Between May 2011 and May 2014, the CVE database~\cite{cve-database} lists
83 vulnerabilities when searching for the string ``ZIP''. Of these, 42
were completely unrelated to the archive format, for example reporting
vulnerabilities revealing ZIP codes of other users. 26 vulnerabilities
were related to ZIP archives, but not to input processing, such as
trusting arbitrary update ZIP files sent to a server or vulnerabilities
that can be accessed through manipulating files in a ZIP container. This
includes several vulnerabilities allowing another files to replaced while
they are extracted from ZIP files because insufficiently secure temporary
directories are used. Of the 15 remaining vulnerabilities pertaining
to ZIP files, 14 vulnerabilities were related to input processing. The
other vulnerability, which falls outside of Nail's purview, concerns a
ZIP packer choosing a weak legacy cryptosystem even when configured to
use AES.

Nail parsers are immune by design to vulnerabilities like these 14.
Ten of those vulnerabilities are memory corruption attacks, that could
also be avoided by using safer languages.  Most of the buffer overflows
seem to result from inconsistent offset fields being manipulated
without checking.  Because Nail's generated code checks offsets before
reading and does not expose any untrusted pointers to the application,
it protects against memory corruption attacks by design.

@@

A similar attack was used by the fourth vulnerability, the infamous
Android master key bug~\cite{saurik-masterkey} that completely
bypassed Android security through parser inconsistencies between the
ZIP handler that checks signatures for privileged applications and the
ZIP implementations that ultimately extract those files. Thus, valid
application bundles could be modified to include malicious applications
without breaking their signatures. Instead of both components containing
an ad-hoc archive implementation, a single Nail grammar would be reusable
across both implementations.

\paragraph{DNS fuzzing.}

To provide additional assurance that Nail parsers are free of memory
corruption attacks, we ran the DNS fuzzer provided with the Metasploit
framework~\cite{mspframework} on our DNS server, which sent randomly
corrupted DNS queries to our server for 4 hours, during which it did
not crash or trigger the stack or heap corruption detector.
